Adopting agile in the large: motivations, success factors and challenges

### 2014-05-18 journal/article.tex
Editing: Research method

Before proceeding with the database search a number of preliminary searches were
performed. The purpose of the preliminary searches was to create a benchmark of
potentially relevant papers that should be matched by the actual database
search. We started by examining top ranked hits by trivial keywords that the
more complex final search string might miss. Initial searches were made using
keywords that were as general as possible, including ``agile transformation''
and ``large scale agile''. Secondly, a trial keyword search was done in the
selected databases (listed in table \ref{table:databases}) using the following
search string:

@@

From these preliminary searches we compiled a list of 117 possibly relevant
papers that should be matched by the actual database search.

@@

\begin{figure}[b]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/research_process.pdf}
    \caption{Database search as study selection process}
    \label{fig:selectionprocess}
  \end{center}
\end{figure}

@@

We constructed a search string based on the facets \emph{agile software
deveolpment} and \emph{organizational transformation}, as presented in section
\ref{sec:inclusioncriteria}. Preliminary searches had showed that picking
keywords with good precision was difficult. Therefore we decided to exclude the
facet \emph{large scale} from the keyword search, with the consequence of
increasing the manual filtering effort in the subsequent steps. Also the facet
or \emph{empiricality} could not be represented by keywords. Having a
substantial part of the matches in non-relevant areas such as agile
manufacturing, we included only articles including the term ``software'' or
articles published in relevant conferences. Instead of engineering the search
terms any further, which proved to result in excluding some relevant articles,
we chose to rely more on manual filtering. The resulting facets and keywords are
listed in Table \ref{table:searchterms}.

@@

In the full text filtering step the references of all papers were also examined
for relevance, including 2 referenced papers as primary sources. Most case study
papers used references very scarcely, mostly referencing well known descriptions
of agile methods.

@@

To give direction for code induction seven different code families were
established, as presented in Table \ref{table:codefamilies}. A description
defining scope and examples for codes were defined for each family. The example
codes would not necessarily be used as actual codes, and would not represent the
entire or final scope of the families.

@@

A passage of text that presents any concept relating to the research questions
or the contextual codes becomes a quotation. If the quotation corresponds
closely to a concept that has already been coded the existing code is used.
Otherwise a new code is created, and the code is assigned to one of the
predefined code families. The labels of existing codes may need to be adjusted
when new quotations are assigned. Many codes may be assigned to one quotation
and quotations of different codes may be overlapping.

The length of the text passage that make up a quotation may vary. For the
contextual codes the quoted passage should be of minimal length. For other
quotes the length of the quotation should be long enough to highlight the
context of the concept the quotation, varying from a few sentences to one
paragraph, or even several paragraphs. As an example of context of the
quotation, if a transformation challenge is described by a quotation it would be
good if also the source or resolution of the challenge could be included in the
quoted text passage. Having enough context should broaden the understanding
of the coded concept when looking at the quotation in isolation..

@@

The total accumulated codes and quotations of the integrated deductive and
inductive coding process are presented in Table \ref{table:codecount}. The total
number of quotations is less than the sum of quotations in the categories
because a single quotation may have multiple codes.

@@

The metric of matching themes measures how well the independent researchers are
able to induct similar codes from the source material. As codes are inducted it
is likely that two researchers label similar quotes differently. To overcome
this problem we defined higher level themes under which the individual codes
were organized. Through discussion we made decisions on whether differently
labeled codes could be organized under the same theme or not. Table
\ref{table:codingexperiment} presents the total number of themes the researchers
found in each document, and how many of the themes were matching. We concluded
that on average two of three themes found by one researcher are similarly found
by the other researcher, but one of three themes is not found by the other
researcher.

The metric of quotation overlap measures how well the quotations for similar
codes match between two independent researchers. The intent is to measure how
codes that are deemed similar by their names match in the actual quoted text. On
a scale of 0 to 3 we evaluated the quoted text of codes in each theme that
matched for both researchers, as described in the previous paragraph. A score of
3 was given for matching codes whose quotation content was virtually the same
for both researchers. A score of 2 was given if the quotations were mostly the
same, but other researcher had included one text passage that the other had
missed. A score of 1 was given if roughly half of the quotations were the same.
If the quotations had less similarity than this a score of 0 was given. One code
provided typically 1 to 3 quotations per document. The quotation overlap score
was counted including only codes that had matching themes. We concluded that the
average quotation overlap score was 2.2.

>>>>

Before proceeding with the database search a number of preliminary searches were
performed. The purpose of the preliminary searches was to create a benchmark of
potentially relevant papers that should be matched by the actual database
search, and to evaluate different search strings. We started by examining top
ranked hits by trivial keywords that the more complex final search string might
miss. Initial searches were made using keywords that were as general as
possible, including ``agile transformation'' and ``large scale agile''.
Secondly, a trial keyword search was done in the selected databases (listed in
table \ref{table:databases}) using the following search string:

@@

From these preliminary searches we compiled a list of 117 possibly relevant
papers that the actual database search would be benchmarked against.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/research_process.pdf}
    \caption{Database search as study selection process}
    \label{fig:selectionprocess}
  \end{center}
\end{figure}

@@

We proceeded with constructing a search string based on the facets presented in
section \ref{sec:inclusioncriteria}. However, preliminary searches had showed
that picking keywords with good precision was difficult. Especially the facet
\emph{large scale} was difficult to represent with precise words. Also the facet
of \emph{empiricality} could not sensibly be represented by keywords. We decided
to include only the factets \emph{agile software deveolpment} and
\emph{organizational transformation} in the keyword search, with the consequence
of increasing the manual filtering effort in the subsequent steps.

Having a substantial part of the matches in non-relevant areas such as agile
manufacturing, we included only articles including the term ``software'' or
articles published in relevant conferences. Instead of engineering the search
terms any further, which proved to result in excluding some relevant articles,
we chose to rely more on manual filtering. The resulting facets and keywords are
listed in Table \ref{table:searchterms}.

@@

After the full text filtering step the references of all papers were also
examined for relevance. Most case study papers used references very scarcely,
mostly referencing well known descriptions of agile methods. We included 2
referenced papers in full text analysis.

@@

To give direction for code induction seven different code families were
established on beforehand, as presented in Table \ref{table:codefamilies}. A
description defining scope and examples for codes were defined for each family.
The example codes would not necessarily be used as actual codes, and would not
represent the entire or final scope of the families.

@@

A passage of text that presents any concept relating to the research questions
or the contextual codes becomes a quotation. If the quotation corresponds
closely to a concept that has already been coded the existing code is used.
Otherwise a new code is created, and the code is assigned to one of the
predefined code families. The labels of existing codes may need to be adjusted
when new quotations are assigned. A clarifying description is written for every
code, so that the precise meaning of the codes can be reviewed. Many codes may
be assigned to one quotation and quotations of different codes may be
overlapping.

The length of the text passage that make up a quotation may vary. For the
contextual codes the quoted passage should be of minimal length. For other
quotes the length of the quotation should be long enough to highlight the
context of the concept the quotation, varying from a few sentences to one
paragraph, or even several paragraphs. As an example of context of the
quotation, if a transformation challenge is described by a quotation it would be
good if also the source or resolution of the challenge could be included in the
quoted text passage. Having enough context should broaden the understanding
of the coded concept when looking at the quotation in isolation.

@@

The total number of codes and quotations created in the coding process is
presented in Table \ref{table:codecount}. The total number of quotations is less
than the sum of quotations in the categories because a single quotation may have
multiple codes.

@@

The metric of matching themes measures how well the independent researchers are
able to induct similar codes from the source material. As codes are inducted it
is likely that two researchers label similar quotes differently. To overcome
this problem we defined higher level themes under which the individual codes
were organized. Through discussion we made decisions on whether differently
labeled codes could be organized under the same theme or not. Table
\ref{table:codingexperiment} presents the total number of themes the researchers
found in each document, and how many of the themes were matching. We concluded
that on average two of three themes found by one researcher were similarly found
by the other researcher, but one of three themes was not found by the other
researcher.

The metric of quotation overlap measures how well the quotations for similar
codes match between two independent researchers. The intent is to measure how
well codes that are deemed similar by their names match in the actual quoted
text. We assigned a quotation overlap score for each code in themes that both
researchers had found. A score of 3 was given for matching codes whose quotation
content was virtually the same for both researchers. A score of 2 was given if
the quotations were mostly the same, but other researcher had included one text
passage that the other had missed. A score of 1 was given if roughly half of the
quotation was the same. If the quotations had less similarity than this a score
of 0 was given. One code provided typically 1 to 3 quotations per document. The
quotation overlap score was counted including only codes that had matching
themes. We concluded that the average quotation overlap score was 2.2.
